---
title: "Introduction"
author: "Michael Kuhn"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction to dict

## dict

To get a new, empty dictionary, call the `dict` function:

```{r}
library(dict)
d <- dict()
```

You can then assign items using numbers and strings (and vectors of these) as keys:

```{r}
d[[1]] <- "First entry!"
d[[c(2,3)]] <- 5
d[["a string"]] <- list(A = 1, B = 2)
d[[c("A", "B")]] <- function(x) 1+x
```

...and then retrieve them again:

```{r}
d[[c(2,3)]]
f <- d[[c("A", "B")]]
f(41)
```

Accessing a non-existing key leads to an error:

```{r, error=TRUE}
d[["?"]]
```

However, you can use `d$get` to return `NA` or another default value:

```{r}
d$get("?")
d$get("?", "default")
```

You can access the `keys`, `values`, `items`, and `length`:

```{r}
d$keys()
d$values()
d$items()
d$length()
```

## numvecdict

To get a new, empty dictionary, call the `numvecdict` function:

```{r}
d <- numvecdict()
```

This dictionary only contains vectors of numbers, which you can assign:

```{r}
d[[1]] <- 1
d[[2]] <- c(2,3)
d[["a string"]] <- 1:10
```

You can append numbers to the lists. If you specify a new key, the entry will be generated automatically:

```{r}
d$append_number(1, 2)
d$append_number(2, 3)
d$append_number("answers", 42)
```

Then, you can retrieve the vectors you stored:

```{r}
d$get(1)
d[[2]]
d[["answers"]]
d[["completely new and never seen key"]]
```
